### 2014-02-27 paper/concrete.tex
checkpoint

This isn't trivial, as it is not sound to add arbitrary additional
conditions on evaluation rules.  To see this, consider a contrived
concrete system where we add a premise to a reduction rule that
stops a task based on secret information.  Such a system will
not satisfy non-interference, as it allows other tasks on the
same level to observe the termination of that task and thus the
secret information which was used to decide if the task terminates
or not.
\Red{This last part is written poorly.  Let's do it better, or remove it.}

@@

\Red{Say what do we do here.}

@@

%{
%format tyerase c = "\varepsilon("c")"
%format tyerasef = "\varepsilon"
%format ^ = " "
%format c = "c"
%format c'
%format cc = "\con{"c"}"
%format cc'
%format ac = "\abs{"c"}"
%format ac'
%format finv = f"^{-1}"
%format V = "V"
%format cV = "\con{"V"}"
%format aV = "\abs{"V"}"
%format ~= = "\approx_l"
%format clequiv = "\con{"~="}"
%format alequiv = "\abs{"~="}"
%format creduce = "\con{".->"}"
%format areduce = "\abs{".->"}"
%format creducestar = "\con{".=>"}"
%format areducestar = "\abs{".=>"}"
%format (ap (f) (x)) = f"("x")"
%format .. = "\circ"
%format idf (t) = "id_{"t"}"

\begin{definition}[Information-flow control language]
    An information-flow control language L is a tuple |(C, .->,
    erasef l)|, where $c \in |C|$ is the type of machine configurations, |.->| is a
    reduction relation between machine configurations and |erasef l : C .-> tyerase C|
    is an erasure function parametrized on labels from machine configurations to \emph{erased} machine
    configurations |tyerase C|.  For sequential languages, the
    language is augmented with a set of terminal configuration states $V
    \subseteq |C|$ for which there are no possible further transitions.
\end{definition}

\begin{definition}[$l$-equivalence]
    In a language |(C, .->, erasef l)|, two machine configurations
    |memberf (c, c') C| are considered $l$-equivalent (|c ~= c'|)
    if |erase l c = erase l c'|.
\end{definition}

\newcommand{\con}[1]{\ensuremath{{\color{red} #1}}}
\newcommand{\abs}[1]{\ensuremath{{\color{blue} #1}}}

@@

\begin{definition}[Inclusion of information-flow control languages]
    A language \con{|(C, V, .->, erasef l)|} is included in another
    language \abs{|(C, V, .->, erasef l)|} if there exists a total function |f : tC -> iC| such that
    |f| is a bijection over |l|-equivalences (|cc clequiv cc'| if and only if
    |(ap f cc) alequiv (ap f cc')|),
    preserves values (if |subseteq cc cV| then |subseteq (ap f cc) aV|) and is
    functorial over |.=>| (if
    |cc creducestar cc'| then |(ap f cc) areducestar (ap f cc')|).
\end{definition}

\begin{theorem}[Isomorphism preserves termination insensitive non-interference]
    If a language \con{L} is included in a language \abs{L}, and \abs{L}
    satisfies TINI, then \con{L} satisfies TINI.
\end{theorem}

\begin{proof}
    Shown by transporting configurations and reduction derivations
    from \con{L} to \abs{L}, applying TINI and transporting the resulting
    equivalence back using bijectivity of $f$ over $l$-equivalences.
\end{proof}

@@

\begin{definition}[Isomorphism of information-flow control languages]
    A language \con{|(C, .->, erasef l)|} is
    isomorphic to a language \abs{|iC, .->, erasef l|} are isomorphic if there exist total functions
    |f : tC -> iC| and |finv : iC -> tC| such that |f .. finv = idf tC|, |finv .. f = idf iC|, and |f| and |finv| are
    functorial over both $l$-equivalences (if |cc clequiv
    cc'| then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and if $|ic|\ \ifc{\approx_l}\ |ic'|$ then $f^{-1}$) and
    $|.->|$ (if $|tc|\ \tar{|.->|}\ |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$ and vice versa).
\end{definition}

@@

\begin{proof}
    Shown by transporting configurations and reduction derivations from
    \tar{L} to \ifc{L}, applying TSNI, and then transporting the
    resulting configuration and multi-step derivation back.
\end{proof}
%}

>>>>

Intuitively, there are two scenarios in which non-interference
can be violated when restricting the transition relation:
\begin{itemize}
  \item Adding an additional premise to one of the rules that inspects
  information which is above the security label of the task currently
  executing.  This would allow another task to observe the termination
  of the other if both are at the same security level, and thus observe
  the secret information that was used in the additional
  premise of the rule.
  \item Adding additional restrictions to transition rules can
  also cause the whole configuration to get stuck, which can leak
  information through the termination channel.
\end{itemize}

%This isn't trivial, as it is not sound to add arbitrary additional
%conditions on evaluation rules.  To see this, consider a contrived
%concrete system where we add a premise to a reduction rule that
%stops a task based on secret information.  Such a system will
%not satisfy non-interference, as it allows other tasks on the
%same level to observe the termination of that task and thus the
%secret information which was used to decide if the task terminates
%or not.

@@

To formalize the conditions under which we can show the concrete
semantics preserve non-interference, we require some notation:

\Red{isomorphism definition here}

Now, we propose the following two-step process to ensure that
TSNI is preserved:
\begin{enumerate}
  \item First, any of the reduction rules of the abstract
  semantics presented in Section~\ref{sec:retrofit} can
  be restricted by adding a predicate $P$ to the premise of
  any rule other than \textsc{I-noStep}.  The predicate $P$
  can depend only on the \textit{erased} configuration
  |erase il ic|, where |il| is the label of the first task
  in the task list.
\end{enumerate}

We now have a concrete semantics, which both uses a different
representation for some of the constructs in language (a single
heap rather than a heap per task in our running example), as well
as restricting some of the operational rules to disallow
undesirable transitions.  To show that the concrete semantics
still satisfy TSNI, we use two techniques.  First, we give a
condition on what kind of restrictions can be allowed on the
operational rules.  Secondly, we define the notation of an
isomorphism between IFC languages and show that it preserves
non-interference.

@@

@@

\begin{definition}[Inclusion of information-flow control languages]
    A language $(|tC|, |tC|^*, \tar{|V|}, \tar{|.->|}, \tar{|erasef l|})$ is
    included in $(|iC|, |iC|^*, \ifc{|V|}, \ifc{|.->|}, \ifc{|erasef
    l|})$ if there exists a total function $f : |tC -> iC|$ such that
    $f$ is a bijection over $l$-equivalences ($|tc|\ \tar{\approx_l}\
    |tc'|$ if and only if $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$),
    preserves values (if $|tc| \subseteq \tar{|V|}$ then $|ic| \subseteq
    \ifc{|V|}$) and is functorial over $|.->|$ (if $|tc|\ \tar{|.->|}\
    |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$).
\end{definition}

\begin{theorem}[Isomorphism preserves termination insensitive non-interference]
    If \tar{L} is included in \ifc{L}, and \ifc{L} satisfies TINI, then
    \tar{L} satisfies TINI.
\end{theorem}

\begin{proof}
    Shown by transporting configurations and reduction derivations
    from \tar{L} to \ifc{L}, applying TINI and transporting the resulting
    equivalence back using bijectivity of $f$ over $l$-equivalences.
\end{proof}

@@

\begin{definition}[Isomorphism of information-flow control languages]
    A language $(|tC|, |tC|^*, \tar{|.->|}, \tar{|erasef l|})$ is
    isomorphic to \ifc{L} $(|iC|, |iC|^*, \ifc{|.->|}, \ifc{|erasef l|})$ are isomorphic if there exist total functions
    $f : |tC -> iC|$ and $f^{-1} : |iC -> tC|$ such that $f \circ f^{-1}
    = id_{|tC|}$, $f^{-1} \circ f = id_{|iC|}$, and $f$ and $f^{-1}$ are
    functorial over both $l$-equivalences (if $|tc|\ \tar{\approx_l}\
    |tc'|$ then $f(|tc|)\ \ifc{\approx_l}\ f(|tc'|)$ and vice-versa) and
    $|.->|$ (if $|tc|\ \tar{|.->|}\ |tc'|$ then $f(|tc|)\ \ifc{|.->|}\ f(|tc'|)$ and vice versa).
\end{definition}

@@

\begin{proof}
    Shown by transporting configurations and reduction derivations from
    \tar{L} to \ifc{L}, applying TSNI, and then transporting the
    resulting configuration and multi-step derivation back.
\end{proof}
